Delayed dichromatism as a convenient tool to disentangle the effects of survival and productivity on the population dynamics in waterfowl

### 2024-05-29 Code/Draft_ruddy_duck_vital_rates.Rmd
Section references update

```{=tex}
\begin{equation}
SI_{i, t} \sim {\sf Binom}(p(re)_{i, t}, S_{i, t})
(\#eq:pis)
\end{equation}
```
## Assessing the effects of culling strategies {#HARV}

During the period when culling pressure was high (i.e. from 2006 onwards), eradication strategies in Great Britain and France differed. In Great Britain, most individuals were culled in winter (53.4% of adults were culled before 30 May), whereas in France, most individuals were culled during the breeding season (81.6% of adults were culled after 30 May). We investigated whether these strategies had different effects on the populations by comparing the resulting growth rates and the relative contributions of both vital rates to them (by comparing the average values during the period of high culling pressure with proxies for the maximum vital rates estimated when both populations reached their maximum growth, see Section \@ref(VAL)). In France, a LIFE project was implemented from 2019 to intensify the culling pressure, especially in winter and spring. We therefore excluded the FR time series from 2019 onwards in order to compare homogeneous culling strategies.

@@

We used the Bayesian framework to implement all submodels presented in Section \@ref(MM). The Bayesian framework is both straightforward and efficient in propagating error through the parameters. We used uninformative priors for all parameters. Since the maximum growth rate is a life history trait expected to be stable between populations of the same species, we used an uninformative hierarchical prior for this parameter. We generated three chains of length 500,000, with a thinning of 10 to avoid autocorrelation in the samples, and discarded the first 2,000 samples as burn-in. We checked the chain convergence using the Gelman and Rubin convergence diagnostic (R\<1.1, @Gelman1992). The models were fitted using NIMBLE [@Valpine2017] run from R [@RCT2022]. The values **X[Y; Z]** reported in Results section are the medians and the corresponding limits of the 95% confidence interval of the posterior distributions. We preferred the median to the mean because it is more robust to skewed distributions.

>>>>

```{=tex}
\begin{equation}
SI_{i, t} \sim {\sf Binom}(p(re)_{i, t}, S_{i, t})
(\#eq:pis)
\end{equation}
```
## Assessing the effects of culling strategies

During the period when culling pressure was high (i.e. from 2006 onwards), eradication strategies in Great Britain and France differed. In Great Britain, most individuals were culled in winter (53.4% of adults were culled before 30 May), whereas in France, most individuals were culled during the breeding season (81.6% of adults were culled after 30 May). We investigated whether these strategies had different effects on the populations by comparing the resulting growth rates and the relative contributions of both vital rates to them (by comparing the average values during the period of high culling pressure with proxies for the maximum vital rates estimated when both populations reached their maximum growth, see previous section). In France, a LIFE project was implemented from 2019 to intensify the culling pressure, especially in winter and spring. We therefore excluded the FR time series from 2019 onwards in order to compare homogeneous culling strategies.

@@

We used the Bayesian framework to implement all submodels presented in Materials & methods section. The Bayesian framework is both straightforward and efficient in propagating error through the parameters. We used uninformative priors for all parameters. Since the maximum growth rate is a life history trait expected to be stable between populations of the same species, we used an uninformative hierarchical prior for this parameter. We generated three chains of length 500,000, with a thinning of 10 to avoid autocorrelation in the samples, and discarded the first 2,000 samples as burn-in. We checked the chain convergence using the Gelman and Rubin convergence diagnostic (R\<1.1, @Gelman1992). The models were fitted using NIMBLE [@Valpine2017] run from R [@RCT2022]. The values **X[Y; Z]** reported in Results section are the medians and the corresponding limits of the 95% confidence interval of the posterior distributions. We preferred the median to the mean because it is more robust to skewed distributions.
